Data Exploration quad maps: IUCN and AquaMaps

### 2016-01-12 data_explore/data_explore_quadmaps.Rmd
need to update the Rmd header on this - output info

---
title: 'Data Exploration quad maps: IUCN and AquaMaps'
output: html_document
---

@@

  cat(sprintf('%s: %s', spp_quad, spp))
  spp_plot <- plot_rangemap(spp)
  print(spp_plot)
  }

>>>>

---
title: 'Data Exploration quad maps: IUCN and AquaMaps'
output: pdf_document
---

@@

  spp_plot <- plot_rangemap(spp)
  spp_plot <- spp_plot + 
    labs(title = sprintf('%s: %s', spp_quad, spp))

  print(spp_plot)
  }
